### 2024-03-02 presentation/parts/presentation_introduction.tex
WIP

\begin{frame}
    \frametitle{What is healthcare?}
    \begin{quotation}
        \noindent\centering
        Healthcare is the improvement of health via the \highlight{prevention}, \highlight{diagnosis}, \highlight{treatment}, \highlight{amelioration} or \highlight{cure} of {\color{theme-green}disease}, {\color{theme-green}illness}, {\color{theme-green}injury}, and {\color{theme-green}other physical and mental impairments} in people.
    \end{quotation}

    \note[item]{Machine learning for healthcare can touch on most of these aspects. \cite{abati_conditional_2020}}
\end{frame}

% \begin{frame}
%     \frametitle{Medical dialogue}
%     \begin{figure}
%         \centering
%         \includegraphics[width=0.7\paperwidth]{figures/speech_bubble.pdf}
%     \end{figure}

%     \note[item]{Healthcare sector is a complex system}
% \end{frame}

\begin{frame}[t]
    \frametitle{Medical dialogue - a challenging domain}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            \begin{itemize}
                \item <1> General practitioner
                \item <1> Nurse
                \item <1> Midwife
                \item <1> Emergency medical dispatcher
                \item <1> Paramedic
                \item <1> Emergency room
                \item <1> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \vspace{-2em}
            \begin{figure}[t]
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}

@@

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item <1-> Communication is everywhere in healthcare. 
                \item <1-> It is complex, involving multiple participants, different contexts, and different purposes.
                \vspace{1em}
                \item <2-> \highlight{Adverse events}: Failure of communication is a leading cause of medical error contributing to two out of three adverse events \cite{starmer_changes_2014}.
                \item <2-> \highlight{Preventability}: A considerable fraction of all hospital admissions have preventable adverse outcomes\footnote<2>{9\% to 16.6\% in AU, NZ, UK, DK.} \cite{carver_medical_2024}.
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=0.95\textwidth]{figures/corti_sketch_emergency.png}
            \end{figure}
        \end{column}
    \end{columns}

    \note[item]{So yes communication can be complex and noisy, but what are the consequences?}
    \note[item]{Adverse events are a leading cause of medical error.}
    \note[item]{But many of these are preventable.}
\end{frame}

@@

    % \note[item] Another aspect of medical communication is documentation.
    % \note[item] This is a central part of healthcare.
    \note[item]{Documentation is essential for a number of purposes but is very time-consuming and imperfect}

\end{frame}

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{columns}
        \begin{column}{0.35\textwidth}
            \begin{itemize}
                \item <1-> \highlight{Assist} with documentation.
                \item <1-> \highlight{Augment} communication.
                \item <1-> \highlight{Improve} decision-making.
                \vspace{1em}
                \item <2-> \highlight{Reduce} the impact of medical errors and adverse events.
                \item <2-> \highlight{Free up} time spent on documentation for patient care.
            \end{itemize}
        \end{column}
        \begin{column}{0.65\textwidth}
            \centering
            \includegraphics[width=0.95\textwidth]{figures/corti_sketch_office.png}
        \end{column}
    \end{columns}
\end{frame}

>>>>

\begin{frame}
    \frametitle{What is healthcare?}
    \begin{quotation}
        \noindent\centering
        \textbf{Healthcare} is the improvement of health via the \highlight{prevention}, \highlight{diagnosis}, \highlight{treatment}, \highlight{amelioration} or \highlight{cure} of {\color{theme-green}disease}, {\color{theme-green}illness}, {\color{theme-green}injury}, and {\color{theme-green}other physical and mental impairments} in people.
    \end{quotation}
    \begin{flushright}
        \footnotesize
        --- Wikipedia
    \end{flushright}

    \note[item]{Machine learning for healthcare touches on most of these aspects. Fx:}
    \note[item]{
        \begin{itemize}
            \item \textbf{Prevention} by predicting risk of disease allowing for early intervention.
            \item \textbf{Diagnosis} by detecting stroke in emergency calls.
            \item \textbf{Treatment} by suggesting medication.
            \item Even \textbf{Cure} by helping to find new cures or treatments for diseases.
        \end{itemize}
    }
\end{frame}

\begin{frame}[t]
    \frametitle{Medical dialogue}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            Every interaction within a healthcare system is a form of \highlight{medical dialogue}:
            \begin{itemize}
                \item <1> General practitioner
                \item <1> Nurse
                \item <1> Midwife
                \item <1> Emergency medical dispatcher
                \item <1> Paramedic
                \item <1> Emergency room
                \item <1> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \vspace{-2em}
            \begin{figure}[t]
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}

@@

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item <1-> Communication is everywhere in healthcare. 
                \item <1-> It is complex, involving multiple participants, different contexts, and different purposes.
                \vspace{1em}
                \item <2-> \highlight{Adverse events}: Failure of communication contributes to two out of three adverse events \cite{starmer_changes_2014}.
                \item <2-> \highlight{Preventability}: Many adverse outcomes are preventable \cite{carver_medical_2024}.
                % \footnote<2>{9\% to 16.6\% in AU, NZ, UK, DK.} \cite{carver_medical_2024}.
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=0.95\textwidth]{figures/corti_sketch_emergency.png}
            \end{figure}
        \end{column}
    \end{columns}

    \note[item]{So yes communication can be complex and noisy, but what are the consequences?}
    \note[item]{Failure of communication is a leading cause of adverse events.}
    \note[item]{Adverse events are episodes of medical error that result in harm to the patient.}
    \note[item]{Luckily, many of these are preventable, although exact numbers vary.}
    \note[item]{Better communication could help reduce these numbers.}
\end{frame}

@@

    \note[item]{Another central aspect of medical communication is documentation.}
    \note[item]{Essential for a number of purposes}
    \note[item]{But, it is time-consuming and of varying quality.}
    \note[item]{(Ambulatory $\equiv$ outpatient care, Tertiary $\equiv$ specialized care)}
\end{frame}

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{columns}
        \begin{column}{0.35\textwidth}
            \begin{itemize}
                \item <1-> \highlight{Assist} with documentation.
                \item <1-> \highlight{Augment} communication.
                \item <1-> \highlight{Improve} decision-making.
                \vspace{1em}
                \item <2-> \highlight{Reduce} the impact of medical errors and adverse events.
                \item <2-> \highlight{Free up} time spent on documentation for patient care.
            \end{itemize}
        \end{column}
        \begin{column}{0.65\textwidth}
            \centering
            \includegraphics[width=0.95\textwidth]{figures/corti_sketch_office.png}
        \end{column}
    \end{columns}

    \note[item]{Machine learning can help in many ways.}
    \note[item]{The main goal of augmenting communication is:
        \begin{itemize}
            \item Reduce the impact of medical errors and adverse events.
            \item Free up time spent on documentation for patient care.
        \end{itemize}
    }
\end{frame}
